Identification of protoneutron star g-modes in gravitational-wave data

### 2020-07-14 introduction.tex
More work in the introduction

Common features in the GW signal, that have been interpreted as g modes of the PNS, have been reported in many works \cite{murphy:09, Cerda:2013, mueller:13gw, Yakunin:2015, Kuroda:2016, Andresen:2017}.  Typically, the frequencies associated with the modes rise monotonically with time during the contraction of the PNS. The characteristic frequencies of the modes associated to the PNS make them promising candidates for detection in ground-based interferometers.

\textbf{Mode analysis and relations}\\

\textbf{This paper method description and previous works}\\
\textbf{Previous work in identifying modes from spectrogram}\\
\textbf{Paper organization}\\

>>>>

Common features in the GW signal, that have been interpreted as g modes of the PNS, have been reported in many works \cite{murphy:09, Cerda:2013, mueller:13gw, Yakunin:2015, Kuroda:2016, Andresen:2017}. Typically, the frequencies associated with the modes rise monotonically with time during the contraction of the PNS. The characteristic frequencies of the modes associated to the PNS make them promising candidates for detection in ground-based interferometers. The presence of g-methods in hot PNS has been studied since the end of last century. The oscillation modes related with the surface of hot PNS was first considered by McDermott, van Horn \& Scholl \cite{McDermott:1983}. Additionally, the stratified structure of the PNS allow the presence of different kinds of g-modes related with the core \cite{Reisenegger:1992}. Many posterior works used simplified background neutron star models (equilibrium configurations), to study different variations of the equilibrium system, like rotation \cite{Ferrari:2004}, general relativity \cite{Passamonti:2005}, non-linearities \cite{Dimmelmeier:2006}, phase transition \cite{Kruger:2015} and realistic equation of state \cite{Camelio:2017}. Sotani \& Takiwaki \cite{Sotani:2016} studied the oscillation modes before the explosion using a simplified fits to numerical simulations.

In previous works \cite{Torres:2018, Torres:2019a}, we explore the eigenmode spectrum using as background results of CCSN numerical simulations and the cavity form by the PNS and the shock. We showed that the GW time-frequency distribution correspond with the frequencies of oscillation of different families of p- and g-modes. These works reveal that is posible to perform CCSN asteroseismology and serves as a starting point to carry out inference of astrophysical parameters of PNSs. In this line of research, in \cite{Torres:2019b} we derived the relations between the different types of modes with some with the evolution of mass and radius of the PNS. These relations are universal in the sense that they not depend of the EOS, the mass of the progenitor or the code used to perform the simulation.

In this paper, we present a method to extract from the GW data the mass and the radius of the PNS as function of time using the universal relations. We inject a GW signal, obtained from a 2D CCSN simulation, into simulated non-white Gaussian noise which spectrum follows the AdLIGO sensitivity curve. We show how the algorithm is able to extract the time-frequency evolution of the main arc of GW emission, which corresponds to the $^2\rm{g}_2$, according to the nomenclature used in \cite{Torres:2019b}. Then the universal relation for this mode is inverted to obtain the time evolution of the ratio $r=M_{\rm PNS}/R_{\rm PNS}^2$. The evolution of the estimated ratio and the true ratio obtained from the simulation is remarkably similar.

\textbf{Paper organisation}\\
